1. vs-code is not connectded Localhost => MongoDB community server install.
2. /*###<< part-2 >>>><<<< Database Related Methods ????????????????????? */
/*
@@ db.createCollection()
@@ db.collectionName.drop()

1. db.help()
2. db.hostInfo()
3. db.getName()
4. db.getMongo()
5. db.currentOp()
6. db.dropDatabase()
7. db.getCollectionInfos()
8. db.getCollectionNames()
9. db.getLastErrorObj()
10. db.inMaster()
11. db.getReplicationInfo()
12. db.logout()
13. db.printCollectionStats()
14. db.serverBuildInfo()
15. db.serverStatus() 
16. db.shutdownServer()  
17. db.stats()
18. db.version()
19. db.createCollection()
20. db.collectionName.drop()
*/

####<< Epi-16 >>>><<<< Comparison Query Operator >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>> 

1. $eq => Equal 
2. $lt => less Then 
3. $lte => less Then Equal
4. $gt => Geater Then
5. $gte => Geater Then Equal
6. $ne => Not Equal
7. $in = in Operator
8. $nin => Not in Operator

/*####<< Epi-18 >>>><<<< Comparison Query Operator >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>> */
/* 
1. $and => Longical AND Operator
2. $or => Logincal OR Operator
3. $not => Logical NOT Operator
4. $nor => Logical Operator
*/

/*####<< Epi-19 >>>><<<< Element query operator >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>> */

Type-----------------------------Number----------------------Atlas--------------------------> 
Double-----------------------------1--------------------------"double"------------------------>
String-----------------------------2--------------------------String------------------------>
Object-----------------------------3--------------------------Object------------------------>
Array------------------------------4--------------------------Array------------------------>
Binary Data------------------------5--------------------------binData------------------------>
ObjectId---------------------------7--------------------------ObjectId------------------------>
Boolean----------------------------8--------------------------bool------------------------>
Date-------------------------------9--------------------------"date"------------------------>
Nul--------------------------------10--------------------------"null"------------------------>
Regular expression-----------------11--------------------------"regex"------------------------>
32-bit integer----------------------16--------------------------"int"------------------------>
Timestamp---------------------------17--------------------------"timestamp"------------------------>
64-bitinteger -----------------------18--------------------------"long"------------------------>
Decimal128-----------------------------19--------------------------decimal------------------------>
